Titeln på avhandlingens språk

### 2023-03-30 body/part1/chapter1-introduction/introduction.tex
intro abstract

% \subsection{Structure of this dissertation}

>>>>

We validate our approach by example, exploring an initial applications of it to \gls{NCS}, and a deeper, more thorough application of it to \gls{WCA}.
For the latter, we develop the first-ever model for emulating human timing behavior \gls{WCA}, created through a comprehensive human-subject study that characterizes these behaviors.
We use our methodology and this model to explore the optimization potential of \gls{WCA} deployments.
Specifically, they investigate the sampling and energy consumption behaviors of these systems with and without considering realistic human behavior, and conclude that significant improvements can be achieved by incorporating our model.
Overall, our results showcase the utility of our methodology, and the importance of considering human behavior in the design and optimization of \gls{WCA} systems to achieve maximum benefits.
